Analysis for Project

### 2021-11-23 analysis/analysis.Rmd
Restructure headers in analysis.Rmd

# Model building time

All models are estimated as logit models.

@@

Now lets run the full models. Warning, the code chunks below take a bit of time to run!

@@

The model results themselves are not that useful directly. I want to compare each multiracial group to:

@@

## AMEs for single race groups

For the paper, I want a table showing the changes across single race groups. Lets go ahead and build that here based on the AMEs.

The results indicate that controlling for everything in model 5 reduces the racial disparities substantially. Comparing Model 5 to Model 2, the controls cut the effect in half for the Black and Indigenous groups. It has less effect and slightly increases the gap for Asians because Asians already had lower rates than Whites. The biggest change is for Latinos. In model 2, Latinos had the second highest probabilities and were 2% higher than whites. After controlling for everything, that actually reverse direction, such that Latinos have slightly lower expected probabilities than whites (.3% less).

# Sensitivity tests

## Models by grade

@@

## Models with stricter parent linking

>>>>

# Model building

## Functional form of year-grade interactions

@@

## Running the models

All models are estimated as logit models. Warning, the code chunks below take a bit of time to run!

@@

## Differences for monoracial groups

The model results here are not very interesting directly because everything is relative to a single reference group. However, before proceeding with a technique for understanding the outcomes for biracial respondents, its worthwhile to look more closely at the differences between monoracial groups. The table below shows these differences using average marginal effects (AME) with whites as the reference.

The results indicate that controlling for everything in Model 5 reduces the racial disparities substantially. Comparing Model 5 to Model 2, the controls cut the effect in half for the Black and Indigenous groups. It has less effect and slightly increases the gap for Asians because Asians already had lower rates than Whites. The biggest change is for Latinos. In model 2, Latinos had the second highest probabilities and were 2% higher than whites. After controlling for everything, that actually reverse direction, such that Latinos have slightly lower expected probabilities than whites (.3% less).

## Average adjusted preditions for biracials

I want to compare each multiracial group to:

@@

## Sensitivity tests

### Models by grade

@@

### Models with stricter parent linking
